\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
	\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
	\item\small{
		\textbf{#1}{: #2 \vspace{-2pt}}
	}
}

\newcommand{\resumeSubheading}[4]{
	\vspace{-1pt}\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{\small#3} & \textit{\small #4} \\
	\end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
	\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
	\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
	
	%----------HEADING-----------------
	\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
		\textbf{\href{https://www.linkedin.com/in/ruben-viscomi-640856197/}{\Large Ruben Viscomi}} & Email : \href{mailto:ruben.viscomi@gmail.com}{ruben.viscomi@gmail.com}\\
		\href{https://www.linkedin.com/in/ruben-viscomi-640856197/}{https://www.linkedin.com/in/ruben-viscomi-640856197} & Mobile : +39-392-244-7315 \\
		\href{https://github.com/ruben-viscomi}{https://github.com/ruben-viscomi}
	\end{tabular*}
	
	
	%-----------EDUCATION-----------------
	\section{Education}
	\resumeSubHeadingListStart
	\resumeSubheading
	{UNICAL - Univeristy of Calabria}{Arcavacata (CS), Italy}
	{Computer Engineering (Computer Science);  GPA: N/A (Dropout)}{Oct. 2017 -- Mar. 2018}
	\resumeSubheading
	{ITT Malafarina}{Soverato (CZ), Italy}
	{Computer Expert (High School Diploma);  GPA: 3.84 (96/100)}{Sep. 2012 -- Jul. 2017}
	\resumeSubHeadingListEnd
	
	
	%-----------EXPERIENCE-----------------
	\section{Experience}
	\resumeSubHeadingListStart
	
	\resumeSubheading
	{Efficy}{Tervuren, Belgium}
	{R\&D Software Engineer}{29\textsuperscript{th} Sep. 2022 - Present}
	\resumeItemListStart
	\resumeItem{Efficy U (Frontend) - Project Management (feature)}
	{Support to Sprints and various filters for the list view. Optimized the time complexity of most of the functions of the Project Management composable from exponential to linear (In the best case i was able to drop the computation time for 10.000 elements from 44.2 seconds to 80 milliseconds) sometimes through the use of custom tailored versions of well known algorithms like Breadth First Search.}
	\resumeItem{Efficy U (Frontend) - Task Scheduler Admin Dashboard (feature)}
	{Dashboard to display all the logs related to the runs of the scheduled tasks}
	\resumeItem{Efficy U (Backend) - Kanban (feature)}
	{Full implementation of the persistence module for the kanban definition. I reduced the payload sent by the fronted (compared to similar features) by implementing an algorithm that calculates the final payload. I made possible to use both conventional or the 'optimized' version of the payload.}
	\resumeItem{Efficy U (Backend) - Card (Kanban sub-feature)}
	{Despite being a sub-feature of the Kanban, this was way more complex. I've totally built this module to be as flexible as possible. The same approach to the kanban was used.}
	\resumeItemListEnd
	
	
	\resumeSubHeadingListEnd
	
	
	%-----------PROJECTS-----------------
	%\section{Projects}
	%\resumeSubHeadingListStart
	%\resumeSubItem{Pooltapes}
	%{implementation of video on demand platform using microservice architecture}
	%\resumeSubHeadingListEnd
	
	%
	%--------PROGRAMMING SKILLS------------
	\section{Programming Skills}
	\resumeSubHeadingListStart
	\item{\textbf{Languages}{: Kotlin, TypeScript, C++, Java, SQL, NoSQL, Rust, Solidity}}
	\item{\textbf{Frameworks}{: Ktor, Vue 3, NestJS, Angular 2+, NextJS, ReactJS, Svelte}}
	\resumeSubHeadingListEnd
	
	
	%
	%-----------------LANGUAGES-----------------
	\section{Languages}
	\resumeSubHeadingListStart
	\item{\textbf{Italian}{: Native speaker}}
	\item{\textbf{English}{: Professional}}
	\item{\textbf{Spanish}{: Basic}}
	\resumeSubHeadingListEnd
	
	
	%-------------------------------------------
\end{document}